---
title: "Spatial Drivers of Fire Intensity"
output:
  html_document:
    keep_md: true
    theme: journal
    fig_caption: true
    fig.path: 'figure_rmd/'
---


```{r set_options, echo=FALSE, warning=FALSE,message=FALSE}
library(knitr)
library(sp)
library(boot)

opts_chunk$set( fig.path = 'figure_rmd/', fig.height = 8, fig.width = 12 )

# Notify that you want to use the counter,
# if you set the counter to 3 then it will use 
# that as starting number. You can also use strings
# if you for instance have a split figure with 
# a "1a" and "1b" setup
options(figure_counter = TRUE)
 
# If you want roman letters then set: 
# options(figure_counter_roman = TRUE)
 
# Evaluate the figure caption after the chunk, 
# sometimes you want to calculate stuff inside the
# chunk that you want to include in the caption and
# it is therefore useful to evaluate it afterwards.
opts_knit$set(eval.after='fig.cap')
 
# The actual hook
knit_hooks$set(plot = function(x, options) {
  fig_fn = paste0(opts_knit$get("base.url"), 
                  paste(x, collapse = "."))
 
  # Some stuff from the default definition
  fig.cap <- knitr:::.img.cap(options)
 
  # Style and additional options that should be included in the img tag
  style=c("display: block",
          sprintf("margin: %s;",
                   switch(options$fig.align, 
                          left = 'auto auto auto 0', 
                          center = 'auto',
                          right = 'auto 0 auto auto')))
  # Certain arguments may not belong in style, 
  # for instance the width and height are usually
  # outside if the do not have a unit specified
  addon_args = ""
 
  # This is perhaps a little overly complicated prepared 
  # with the loop but it allows for a more out.parameters if necessary
  if (any(grepl("^out.(height|width)", names(options)))){
      on <- names(options)[grep("^out.(height|width)", names(options))]
      for(out_name in on){
          dimName <- substr(out_name, 5, nchar(out_name))
          if (grepl("[0-9]+(em|px|%|pt|pc|in|cm|mm)", out_name))
              style=append(style, paste0(dimName, ": ", options[[out_name]]))
          else if (length(options$out.width) > 0)
              addon_args = paste0(addon_args, dimName, "='", options[[out_name]], "'")
      }
  }
 
  # Add counter if wanted
  fig_number_txt <- ""
  cntr <- getOption("figure_counter", FALSE)
  if (cntr != FALSE){
    if (is.logical(cntr))
      cntr <- 1
    # The figure_counter_str allows for custom 
    # figure text, you may for instance want it in
    # bold: <b>Figure %s:</b>
    # The %s is so that you have the option of setting the
    # counter manually to 1a, 1b, etc if needed
    fig_number_txt <- 
      sprintf(getOption("figure_counter_str", "Figure %s: "), 
              ifelse(getOption("figure_counter_roman", FALSE), 
                     as.character(as.roman(cntr)), as.character(cntr)))
 
    if (is.numeric(cntr))
      options(figure_counter = cntr + 1)
  }
 
  # Put it all together
  paste0("<figure><img src='", fig_fn, "'", 
         " ", addon_args,
         paste0(" style='", paste(style, collapse="; "), "'"),
         ">",
         "<br><figcaption>", fig_number_txt, fig.cap, "</figcaption></figure><br>")
})

```


We don't know much about what drives fire intensity across different scales. To address this, fire radiative power data were obtained from [FIRMS](https://earthdata.nasa.gov/data/near-real-time-data/firms) for the period 1 Jan 2004 to 1 Jan 2014.

Data were subset to only include fire detections of > 95% confidence.

Fire detections were then associated with:
* Mean annual precipitation
* Geologic parent material
* Woody cover

**Methods**
```{r SetUp, echo=FALSE,warning=FALSE,message=FALSE}

library(gridExtra)
library(ggthemes)
library(stargazer)
library(rasterVis)
library(ggplot2)

setwd("/Users/danielgodwin/Dropbox/Graduate School/Dissertation/Chapter 2 - Ignition Variation/SpatialDriversofTopKill")

textSize = 14
myTheme <- theme_tufte() +
  theme(
    text = element_text(size=textSize,family="sans"),
    axis.line = element_line(size = .3)
  )
```
Run the analyses related to the fire radiative power detections.

```{r RunScript,echo=TRUE, warning=FALSE,message=FALSE,include=TRUE,tidy_source=TRUE}
source("Scripts/FIRMS_Map.R",echo=FALSE,verbose = FALSE)
```
Run the model as it relates to predicting intensity.
```{r RunModel,echo=TRUE, warning=FALSE,message=FALSE,include=TRUE,tidy_source=TRUE}
source("Scripts/IntensityMap.R",echo=FALSE,verbose = FALSE)
```
Run the Fire Scar Analysis
```{r RunAnalysis,echo=TRUE, warning=FALSE,message=FALSE,include=TRUE,tidy_source=TRUE}
source("Scripts/FireScar_Analysis.R",echo=FALSE,verbose = FALSE)
```
Run the intensity model analysis
```{r RunMap,echo=TRUE, warning=FALSE,message=FALSE,include=FALSE,tidy_source=TRUE}
source("Scripts/MAP_WC.R",echo=FALSE,verbose = FALSE)
```

**Figures**

```{r logicalFramework,echo=FALSE,warning=FALSE,message=FALSE,fig.cap=""}

a_map_pwc <- ggplot()+
  myTheme+
  coord_cartesian()+
  theme(plot.title = element_text(size=12,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
        legend.position=c(.8,.9),legend.direction="vertical")+
  ggtitle("A.")+
  xlab("Mean Annual Precipitation")+
  ylab("Woody Cover (%)")+
  ylim(0,50)+
  xlim(0,1000)+
  #geom_point(data=krugerMAP_agg,aes(y = WoodyCover, x = MAP_cut), size=1,width=1)+
  geom_pointrange(data=krugerMAP_agg,aes(y = WoodyCover,ymax = WoodyCover + WC_SE,ymin = WoodyCover - WC_SE, x = MAP_cut), size=.5)+
  geom_abline(slope = coef(WCMap)[2], intercept = coef(WCMap)[1])

b_map_fuel_accumulation <- ggplot()+
  myTheme+
  coord_cartesian()+
  theme(plot.title = element_text(size=12,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
        legend.position=c(.8,.9),legend.direction="vertical")+
  ggtitle("B.")+
  xlab("Mean Annual Precipitation")+
  ylab(expression(paste("Fuel Load (kg ha",{}^{-1},")")))+
  ylim(0,6000)+
  xlim(0,1000)+
  geom_abline(slope = 6000/1250, intercept = 0)

c_intensity_fuel_accumulation <- ggplot()+
  myTheme+
  coord_cartesian()+
  theme(plot.title = element_text(size=12,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
        legend.position=c(.8,.9),legend.direction="vertical")+
  ggtitle("C.")+
  xlab(expression(paste("Fuel Load (kg ha",{}^{-1},")")))+
  ylab("Fire Intensity")+
  ylim(0,3000)+
  xlim(0,6000)+
 # geom_abline(slope = 16890 * .1 * .04 / 1000, intercept = 0,linetype="dashed")+
  geom_abline(slope = 16890 * .1 * .38 / 1000, intercept = 0,linetype="solid")
 # +geom_abline(slope = 16890 * .1 * 1.22 / 1000, intercept = 0,linetype="dashed")
  

d_map_intensity <- ggplot()+
  myTheme+
  coord_cartesian()+
  theme(plot.title = element_text(size=12,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
        legend.position=c(.8,.9),legend.direction="vertical")+
  ggtitle("D.")+
  xlab("Mean Annual Precipitation")+
  ylab(expression(paste("Fire Intensity (kW ","m",{}^{-1},")")))+
  ylim(0,3000)+
  xlim(0,1000)+
  geom_abline(slope = 4.13, intercept = -558.22)

dummyDF <- data.frame(MAP = seq(0,1200,10))
dummyDF$Intensity <- dummyDF$MAP * 4.13 - 558.22
dummyDF$ProbTop <- inv.logit(-3.9 * log(2) + .05 * sqrt(dummyDF$Intensity) + .3 * 1)


e_map_intensity <- ggplot()+
  myTheme+
  coord_cartesian()+
  theme(plot.title = element_text(size=12,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
        legend.position=c(.8,.9),legend.direction="vertical")+
  ggtitle("E.")+
  xlab("Mean Annual Precipitation")+
  ylab("Probability of Top Kill")+
  ylim(0,1)+
  xlim(0,1000)+
  geom_line(data = dummyDF, aes(x = MAP, y = ProbTop))

grid.arrange(a_map_pwc,b_map_fuel_accumulation,c_intensity_fuel_accumulation,d_map_intensity,e_map_intensity,nrow=3)
  
```
A. Average woody cover by mean annual precipitation at 50 mm/yr intervals (points); line is significant at P < 0.01, R^2 = 0.5862. B. Relationship between fuel load accumulation (grass biomass) and mean annual precipitation, derived from Figure 1, Govender et al. 2006. C. Relationship between fireline intensity and fuel load given an average rate of spread of .04 m/s. D. Relationship between average fireline intensity and mean annual precipitation, from Figure 2, Govender et al. 2006. E. Probability of top kill as a function of fire intensity by mean annual precipitation, as a function of Higgins et al. 2011 and the relationship shown in D.


```{r FRP_by_MAP_Season,echo=FALSE,warning=FALSE,message=FALSE,fig.cap="Fire radiative power by mean annual precipitation, subdivided by (A.) season of burn and (B.) geologic parent material."}
fireSeasonMap <- ggplot(data=FRP_Variables,aes(x=MAP,y=FRP,color=Season))+
  myTheme+
  ggtitle("A.")+
     theme(plot.title = element_text(size=12,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
         legend.position=c(.8,.9),legend.direction="vertical")+
  ylab(expression(paste("Fire Radiative Power (MW ","km",{}^{-2},")")))+
  xlab(expression(paste("Mean Annual Precipitation (mm ","yr",{}^{-1},")")))+
  scale_color_colorblind()+
  
  geom_point(alpha=.75)

fireGLYMap <- ggplot(data=FRP_Variables,aes(x=MAP,y=FRP,color=Geology))+
  ggtitle("B.")+
  myTheme+
     theme(plot.title = element_text(size=12,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
         legend.position=c(.8,.9),legend.direction="vertical")+
  ylab(expression(paste("Fire Radiative Power (MW ","km",{}^{-2},")")))+
  xlab(expression(paste("Mean Annual Precipitation (mm ","yr",{}^{-1},")")))+
  scale_color_colorblind()+
  geom_point(alpha=.75)

grid.arrange(fireSeasonMap,fireGLYMap,nrow=1)
```

```{r FRP_by_WoodyCover,echo=FALSE,warning=FALSE,message=FALSE,fig.cap="Fire radiative power by percent woody cover, subdivided by (A.) season of burn and (B.) geologic parent material."}
fireSeasonWC <- ggplot(data=FRP_Variables,aes(x=WoodyCover,y=FRP,color=Season))+
  myTheme+
     theme(plot.title = element_text(size=12,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
         legend.position=c(.8,.9),legend.direction="vertical")+
  ylab(expression(paste("Fire Radiative Power (MW ","km",{}^{-2},")")))+
  xlab("Woody Cover (%)")+
  xlim(0,100)+
  ggtitle("A.")+
  scale_color_colorblind()+
  geom_point(alpha=.75)

fireGLYWC <- ggplot(data=FRP_Variables,aes(x=WoodyCover,y=FRP,color=Geology))+
  myTheme+
     theme(plot.title = element_text(size=12,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
         legend.position=c(.8,.9),legend.direction="vertical")+
  ylab(expression(paste("Fire Radiative Power (MW ","km",{}^{-2},")")))+
  xlab("Woody Cover (%)")+
  xlim(0,100)+
  ggtitle("B.")+
  scale_color_colorblind()+
  geom_point(alpha=.75)

grid.arrange(fireSeasonWC,fireGLYWC,nrow=1)
```

```{r FRP_by_GLY,echo=FALSE,warning=FALSE,message=FALSE,fig.cap="Fire radiative power by geology and season of burn."}
fireGly <- ggplot(data=FRP_Variables,aes(x=Geology,y=FRP))+
  myTheme+
  xlim("Granitic","Basaltic")+
  ylab(expression(paste("Fire Radiative Power (MW ","km",{}^{-2},")")))+
  xlab("Parent Material")+
  scale_color_colorblind()+
  geom_boxplot()

fireSeason <- ggplot(data=FRP_Variables,aes(x=Season,y=FRP))+
  myTheme+
  ylab(expression(paste("Fire Radiative Power (MW ","km",{}^{-2},")")))+
  xlab("Parent Material")+
  scale_color_colorblind()+
  geom_boxplot()

grid.arrange(fireGly,fireSeason,nrow=1)
```

```{r FRP_avg_by_MAP,echo=FALSE,warning=FALSE,message=FALSE,fig.cap="Fire radiative power, averaged by 50 mm / yr MAP"}
frp_MAP <- ggplot()+
  myTheme+
  ylab(expression(paste("Fire Radiative Power (MW ","km",{}^{-2},")")))+
   xlab(expression(paste("Mean Annual Precipitation (mm ","yr",{}^{-1},")")))+
  scale_color_colorblind()+
  geom_pointrange(data = FRP_Variables_agg, aes(x = MAP_cut,
                                                y = Intensity,
                                                ymin = Intensity - Intensity_SE,
                                                ymax = Intensity + Intensity_SE))
frp_MAP
```
**Kruskal-Wallis Tests**
```{r kwTables,echo=FALSE,results='markup',tidy=TRUE}
kruskal.test(FRP ~ Geology,FRP_Variables)

kruskal.test(FRP ~ as.factor(Season),FRP_Variables)
```

No significant difference by seasonality, but there is a difference by geologic parent material.



```{r ModeledFirelineIntensity,echo=FALSE,warning=FALSE,message=FALSE,fig.cap="Modeled fireline intensity across Kruger National Park"}

intensityAt <- c(0,1000,2000,4000,6000,8000)
intensityLabels <- c("",
  expression(paste("Very low (< 1000 kJ ","s",{}^{-1},"m",{}^{-1},")")),
  expression(paste("Low (1000 - 2000 kJ ","s",{}^{-1},"m",{}^{-1},")")),
  expression(paste("Moderate (2000 - 4000 kJ ","s",{}^{-1},"m",{}^{-1},")")),
  expression(paste("High (4000 - 6000 kJ ","s",{}^{-1},"m",{}^{-1},")")),
  expression(paste("Very High (> 6000 kJ ","s",{}^{-1},"m",{}^{-1},")")))

intensityKey <- list(at=intensityAt,
                     labels=list(labels=intensityLabels,
                                 at=intensityAt))

levelplot(krugerFirelineIntensity,
          colorkey=intensityKey,
          labels=FALSE,
          at=intensityAt,
          contour=TRUE,
          margin=FALSE)+
  spplot(krugerOutline,
         fill="transparent",
         colorkey=FALSE)

```

```{r ModeledProbTopKill,echo=FALSE,warning=FALSE,message=FALSE,fig.cap="Modeled probability of topkill of a one meter sapling across Kruger National Park"}
probTop <- -3.9 * log(2) + .05 * sqrt(krugerFirelineIntensity$High) + .3 * 1
probTop$Average <- -3.9 * log(2) + .05 * sqrt(krugerFirelineIntensity$Average) + .3 * 1

probTop <- exp(probTop) / (1+exp(probTop))
names(probTop)[1] <- "High"


levelplot(probTop,
          labels=FALSE,
          contour=TRUE,
          col.regions = terrain.colors,
          colorkey = list(col =  terrain.colors),
          pretty=TRUE,
          margin=FALSE)+
  spplot(krugerOutline,
         fill="transparent",
         colorkey=FALSE)

```

```{r FLI_By_WoodyCover,echo=FALSE,warning=FALSE,fig.cap="Modeled average fireline intensity by percent woody cover and geologic parent material."}

FLI_by_WC <- ggplot(data=krugerIntensityInvestigationDF,aes(y=FirelineIntensity_Average,x=WoodyCover,shape=Geology))+
  myTheme+
  scale_color_colorblind()+
  scale_shape(solid=FALSE)+
  xlim(0,100)+
  
  xlab("Woody Cover (%)")+
  ylab(expression(paste("Fireline Intensity (kJ ","s",{}^{-1},"m",{}^{-1},")")))+
  geom_point(size=1,alpha=.3)+
  facet_wrap(~Geology)

FLI_by_WC
```

```{r FLI_By_MAP,echo=FALSE,warning=FALSE,fig.cap="Modeled fireline intensity by MAP and geologic parent material."}

FLI_by_MAP <- ggplot(data=krugerIntensityInvestigationDF,aes(y=FirelineIntensity_Average,x=MAP,shape=Geology))+
  myTheme+
  scale_color_colorblind()+
  scale_shape(solid=FALSE)+
   xlab(expression(paste("Mean Annual Precipitation (mm ","yr",{}^{-1},")")))+
  ylab(expression(paste("Fireline Intensity (kJ ","s",{}^{-1},"m",{}^{-1},")")))+
  geom_point(size=1,alpha=.3)+
  facet_wrap(~Geology)

FLI_by_MAP
```

```{r FLI_By_NavashniStandards,echo=FALSE,warning=FALSE,fig.cap="Percentage of probable fires by fireline intensity classes, as defined by Govender et al. 2006"}
krugerIntensityInvestigationDF$IntensityCut_High <- cut(krugerIntensityInvestigationDF$FirelineIntensity_High,breaks = c(-500,1000,2000,4000,6000,8000))

krugerIntensityInvestigationDF$IntensityCut_Average <- cut(krugerIntensityInvestigationDF$FirelineIntensity_Average,breaks = c(-500,1000,2000,4000,6000,8000))


levels(krugerIntensityInvestigationDF$IntensityCut_Average) <- c("Very low (< 1000)","Low (1000 - 2000)","Moderate (2000 - 4000)","High (4000 - 6000)","Very Hight (> 6000)")

levels(krugerIntensityInvestigationDF$IntensityCut_High) <- c("Very low (< 1000)","Low (1000 - 2000)","Moderate (2000 - 4000)","High (4000 - 6000)","Very Hight (> 6000)")

krugerIntensityInvestigationDF_High_agg <- ddply(krugerIntensityInvestigationDF,.(IntensityCut_High),summarize,Count = length(FirelineIntensity_High))

krugerIntensityInvestigationDF_High_agg$Percent <- krugerIntensityInvestigationDF_High_agg$Count / sum(krugerIntensityInvestigationDF_High_agg$Count)

krugerIntensityInvestigationDF_Average_agg <- ddply(krugerIntensityInvestigationDF,.(IntensityCut_Average),summarize,Count = length(FirelineIntensity_Average))

krugerIntensityInvestigationDF_Average_agg$Percent <- krugerIntensityInvestigationDF_Average_agg$Count / sum(krugerIntensityInvestigationDF_Average_agg$Count)

names(krugerIntensityInvestigationDF_Average_agg)[1] <- "IntensityCut"
names(krugerIntensityInvestigationDF_High_agg)[1] <- "IntensityCut"
krugerIntensityInvestigationDF_Average_agg$Scenario <- "Average"
krugerIntensityInvestigationDF_High_agg$Scenario <- "High"
krugerIntensityInvestigationDF_agg <- rbind(krugerIntensityInvestigationDF_Average_agg,krugerIntensityInvestigationDF_High_agg)

FLI_Hist <- ggplot(data=krugerIntensityInvestigationDF_agg,aes(x=IntensityCut,y=Percent*100))+
  myTheme+
  ylab("Percentage of Fires (%)")+
 # scale_x_continuous(breaks=c(0,1000,2000,3000,4000,5000),labels=c(""))+
  xlab(expression(paste("Fireline intensity classes (kJ ","s",{}^{-1},"m",{}^{-1},")")))+
  geom_text(aes(label = round(Percent*100,digits=2),y = Percent*100 + 5),parse=TRUE)+
  geom_bar(stat="identity",position="dodge")+
  facet_wrap(~Scenario)

FLI_Hist
```


```{r FLI_By_AvgProbTop,echo=FALSE,warning=FALSE,fig.cap="Probability of Top Kill by Mean Annual Precipitation, modeled."}
krugerIntensityInvestigationDF$MAP_cut <- cut(krugerIntensityInvestigationDF$MAP,breaks=seq(400,950,50))

krugerProbTop_High <- ddply(krugerIntensityInvestigationDF,
                       .(MAP_cut),
                       summarize,
                       Intensity = mean(FirelineIntensity_High),
                       Intensity_SE = sd(FirelineIntensity_High)/sqrt(length(FirelineIntensity_High)))

krugerProbTop_Average <- ddply(krugerIntensityInvestigationDF,
                       .(MAP_cut),
                       summarize,
                       Intensity = mean(FirelineIntensity_Average),
                       Intensity_SE = sd(FirelineIntensity_Average)/sqrt(length(FirelineIntensity_Average)))

levels(krugerProbTop_Average$MAP_cut) <- seq(400,950,50)
krugerProbTop_Average$MAP_cut <- as.character(krugerProbTop_Average$MAP_cut)
krugerProbTop_Average$MAP_cut <- as.numeric(krugerProbTop_Average$MAP_cut)

levels(krugerProbTop_High$MAP_cut) <- seq(400,950,50)
krugerProbTop_High$MAP_cut <- as.character(krugerProbTop_High$MAP_cut)
krugerProbTop_High$MAP_cut <- as.numeric(krugerProbTop_High$MAP_cut)

krugerProbTop_High$ProbTop <- inv.logit(-3.9 * log(2) + .05 * sqrt(krugerProbTop_High$Intensity) + .3 * 1)
krugerProbTop_Average$ProbTop <- inv.logit(-3.9 * log(2) + .05 * sqrt(krugerProbTop_Average$Intensity) + .3 * 1)

krugerProbTop_High$ProbTop_SE <- inv.logit(-3.9 * log(2) + .05 * sqrt(krugerProbTop_High$Intensity_SE) + .3 * 1)
krugerProbTop_Average$ProbTop_SE <- inv.logit(-3.9 * log(2) + .05 * sqrt(krugerProbTop_Average$Intensity_SE) + .3 * 1)

probTop_high <- ggplot()+
  myTheme+
  coord_cartesian()+
  theme(plot.title = element_text(size=12,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
        legend.position=c(.8,.9),legend.direction="vertical")+
  ggtitle("A.")+
  xlab("Mean Annual Precipitation")+
  ylab("Probability of Top Kill (1 m sapling)")+
  ylim(0,1)+
  xlim(0,1000)+
  geom_line(data = krugerProbTop_High, aes(x = MAP_cut, y = ProbTop))+
  geom_line(data = krugerProbTop_High, linetype="dashed",aes(x = MAP_cut, y = ProbTop + ProbTop_SE))+
  geom_line(data = krugerProbTop_High, linetype="dashed",aes(x = MAP_cut, y = ProbTop - ProbTop_SE))

probTop_average <- ggplot()+
  myTheme+
  coord_cartesian()+
  theme(plot.title = element_text(size=12,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
        legend.position=c(.8,.9),legend.direction="vertical")+
  ggtitle("B.")+
  xlab("Mean Annual Precipitation")+
  ylab("Probability of Top Kill (1 m sapling)")+
  ylim(0,1)+
  xlim(0,1000)+
  geom_line(data = krugerProbTop_Average, aes(x = MAP_cut, y = ProbTop))+
  geom_line(data = krugerProbTop_Average, linetype="dashed",aes(x = MAP_cut, y = ProbTop + ProbTop_SE))+
  geom_line(data = krugerProbTop_Average, linetype="dashed",aes(x = MAP_cut, y = ProbTop - ProbTop_SE))

grid.arrange(probTop_high,probTop_average,nrow=1)


```



**Intensity by Woody Cover and MAP: GLM Results**
```{r FLI_WoodyCover_GLM,echo=FALSE,results='asis',warning=FALSE,message=FALSE}
library(texreg)

Null_GLM <- glm(FirelineIntensity_Average ~ 1,data=krugerIntensityInvestigationDF)
Intensity_WC_GLM <- glm(FirelineIntensity_Average ~ WoodyCover,data = krugerIntensityInvestigationDF)
Intensity_MAP_GLM <- glm(FirelineIntensity_Average ~ MAP, data = krugerIntensityInvestigationDF)



htmlreg(l=list(Null_GLM,Intensity_WC_GLM), doctype = F, html.tag = FALSE, inline.css = TRUE, 
    head.tag = FALSE, body.tag = FALSE, center = FALSE, single.row = TRUE, caption = "") 

htmlreg(l=list(Null_GLM,Intensity_MAP_GLM), doctype = F, html.tag = FALSE, inline.css = TRUE, 
    head.tag = FALSE, body.tag = FALSE, center = FALSE, single.row = TRUE, caption = "") 


```

```{r FireScars_by_variables,echo=FALSE,warning=FALSE,fig.cap="Reported impacts of fire."}
firescar_final <- subset(firescar_final,WoodyCover >= 0)
firescar_woodyTable <- ddply(.data=firescar_final,
                             .(WOODYIMPAC,Season),
                             summarize,
                             Count = length(WOODYIMPAC))

firescar_woodyTable <- ddply(.data=firescar_woodyTable,
                             .(Season),
                             transform,
                             Percent = Count/sum(Count))

firescar_herbTable <- ddply(.data=firescar_final,
                             .(HERBACEOUS,Season),
                             summarize,
                             Count = length(HERBACEOUS))

firescar_herbTable <- ddply(.data=firescar_herbTable,
                             .(Season),
                             transform,
                             Percent = Count/sum(Count))

textSize = 15

FireSev_Hist <- ggplot(data=firescar_woodyTable,aes(x=WOODYIMPAC,y=Percent,fill=Season))+
  myTheme+
  ylab("Percent")+
      theme(text = element_text(size=textSize))+
     theme(plot.title = element_text(size=12,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
         legend.position="none",legend.direction="vertical")+
  ggtitle("A.")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlab("Impact on Woody Cover")+
  ylim(0,1)+
  geom_bar(position="dodge",stat="identity")

FireHerb_Hist <- ggplot(data=firescar_herbTable,aes(x=HERBACEOUS,y=Percent,fill=Season))+
  myTheme+
  ylab("Percent")+
      theme(text = element_text(size=textSize))+
     theme(plot.title = element_text(size=12,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
         legend.position=c(.8,.9),legend.direction="vertical")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ggtitle("B.")+
  ylim(0,1)+
  xlab("Impact on Herbaceous Material")+
  geom_bar(position="dodge",stat="identity")

grid.arrange(FireSev_Hist,FireHerb_Hist,nrow=1)
```

```{r FireScars_by_MAP,echo=FALSE,warning=FALSE,fig.cap="Impact on woody cover and herbaceous material by mean annual precipitation (A,B). Relationship between percent woody cover and reported impact on woody cover and herbaceous material (C,D)."}


FireSev_MAP <- ggplot(data=firescar_final,aes(y=MAP,x=WOODYIMPAC))+
  myTheme+
  coord_flip()+
    ylab(expression(paste("Mean Annual Precipitation (mm ","yr",{}^{-1},")")))+
    theme(text = element_text(size=textSize))+
      theme(plot.title = element_text(size=textSize,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
         legend.position=c(.8,.9),legend.direction="vertical")+
  ggtitle("A.")+
  xlab("Impact on Woody Cover")+
  geom_boxplot()

FireHerb_MAP <- ggplot(data=firescar_final,aes(y=MAP,x=HERBACEOUS))+
  myTheme+
  coord_flip()+
  xlab("Impact on Herbaceous Material")+
    theme(text = element_text(size=textSize))+
     theme(plot.title = element_text(size=textSize,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
         legend.position="none",legend.direction="vertical")+
  ggtitle("B.")+
  ylab(expression(paste("Mean Annual Precipitation (mm ","yr",{}^{-1},")")))+  
  geom_boxplot()

FireSev_WC <- ggplot(data=firescar_final,aes(y=WoodyCover,x=WOODYIMPAC))+
  myTheme+
  coord_flip()+
    ylab("Woody Cover (%)")+
    theme(text = element_text(size=textSize))+
      theme(plot.title = element_text(size=textSize,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
         legend.position=c(.8,.9),legend.direction="vertical")+
  ggtitle("C.")+
  xlab("Impact on Woody Cover")+
  geom_boxplot()

FireHerb_WC <- ggplot(data=firescar_final,aes(y=WoodyCover,x=HERBACEOUS))+
  myTheme+
  coord_flip()+
  xlab("Impact on Herbaceous Material")+
  theme(text = element_text(size=textSize))+
     theme(plot.title = element_text(size=textSize,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
         legend.position="none",legend.direction="vertical")+
  ggtitle("D.")+
  ylab("Woody Cover (%)")+  
  geom_boxplot()

grid.arrange(FireSev_MAP,FireHerb_MAP,FireSev_WC,FireHerb_WC,nrow=2)
```

```{r FireSeverityModel,echo=FALSE,include=TRUE,results='asis',warning=FALSE,message=FALSE}
NullWI <- glm(WoodyImpactLevel ~ 1,data=firescar_final)
WC_glm <- glm(WoodyImpactLevel~WoodyCover,data=firescar_final)

htmlreg(l=list(NullWI,WC_glm), doctype = F, html.tag = FALSE, inline.css = TRUE, 
    head.tag = FALSE, body.tag = FALSE, center = FALSE, single.row = TRUE, caption = "") 
```

```{r PreviousMAP,echo=FALSE,warning=FALSE,fig.cap="Role of previous two years of mean annual precipitation on reported impacts on woody species (A.) and herbaceous cover (B.)"}

FireSev_PreMAP <- ggplot(data=firescar_final,aes(y=PreviousMAP,x=WOODYIMPAC))+
  myTheme+
  coord_flip()+
    ylab("Sum of Previous\nTwo Years of Rain (mm)")+
      theme(plot.title = element_text(size=12,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
         legend.position=c(.8,.9),legend.direction="vertical")+
  ggtitle("A.")+
  xlab("Impact on Woody Cover")+
  geom_boxplot()

FireHerb_PreMAP <- ggplot(data=firescar_final,aes(y=PreviousMAP,x=HERBACEOUS))+
  myTheme+
  coord_flip()+
  xlab("Impact on Herbaceous Material")+
     theme(plot.title = element_text(size=12,
                                  hjust="0",
                                  family = "Arial",
                                  face="plain"),
         legend.position="none",legend.direction="vertical")+
  ggtitle("B.")+
  ylab("Sum Previous\nTwo Years of Rain (mm)")+
  geom_boxplot()

grid.arrange(FireSev_PreMAP,FireHerb_PreMAP,nrow=1)
```

[Analyses of Data on Spatial Drivers of Top Kill](http://github.com/danielg7/SpatialDriversOfTopKill/) by Daniel Godwin is licensed under a [Creative Commons Attribution-NonCommercial-NoDerivatives 4.0 International License](http://creativecommons.org/licenses/by-nc-nd/4.0/).